\pkg{webchem}: An \proglang{R} Package to Retrieve Chemical Information from the Web

### 2020-03-26 revision3_2581/paper.tex
update wikidata desc
Removed sentence about only querying chemical identifiers.  Seems like you can query chemical names too, but results may vary.
update description of what webchem returns
webchem does not currently "always return a named list". Based on discussion on the webchem github, I think this change is accurate and will continue to be accurate in the future.

\begin{description}
\item[NIH Chemical Identifier Resolver (CIR)]{\citep{cir} A web
    service that converts from and to various chemical identifiers. The database holds millions of identifier combinations.}
\item[ChemSpider]{\citep{pence_chemspider:_2010} is a free chemical
	structure database providing access to over 67 million
	structures from hundreds of data sources. It provides identifiers, properties and can also be
	used to convert identifiers.}
\item[Chemical Translation Service (CTS)]{
  \citep{Wohlgemuth_Haldiya_Willighagen_Kind_Fiehn_2010} A web
    service that converts from and to various chemical identifiers.}
\item[ETOX]{\citep{etox} Information System Ecotoxicology and
    Environmental Quality Targets by the German Federal Environmental
    Agency. Provides basic identifiers, synonyms, ecotoxicological
    data for over 64,000 entries and quality targets for different countries.}
\item[ChemID\emph{plus}]{\citep{Tomasulo_2002} is a large web-based
	database provided by the National Library of Medicine. It contains
	identifiers, synonyms, toxicological data and chemical
	properties for over 420,000 records.}
\item[OPSIN]{\citep{Lowe_Corbett_Murray-Rust_Glen_2011} The Open
	Parser for Systematic IUPAC nomenclature is a chemical name
	interpreter and provides InChI and SMILES identifiers.}
\item[Compendium of Pesticide Common Names]{\citep{wood} The
	compendium provides information on pesticide common names,
	identifiers and classification. The compendium contains more than 1800 active ingredients and more than 350 ester and salt derivatives. }
\item[Wikidata]{\citep{wiki} Wikipedia contains information for over
	210,000 chemicals
	\citep{Ertl_Patiny_Sander_Rufener_Zasso_2015}. Currently
	\pkg{webchem} can only query chemical identifiers.}
\item[PubChem]{\citep{Kim_2016} PubChem is a public repository for
    information on more than 250 million chemical substances, providing identifiers,
    properties and synonyms. We use an interface to the PUG-REST web
    service \citep{Kim_Thiessen_Bolton_Bryant_2015}.}
\item[PAN Pesticide Database]{ \citep{pan} Information on pesticides --
	provides basic identifiers, ecotoxicological data, chemical
	properties, uses and regulatory status for 6,500 pesticides.}
\item[Flavornet]{\citep{flavornet} Flavornet is a compilation of 738 aroma compounds found in human odor space.}
\item[NIST]{\citep{nist} The NIST Chemistry WebBook provides access to data compiled and distributed by NIST under the Standard Reference Data Program. The WebBook provides chemical and physical property data on over 40,000 compounds.}
\item[ChEBI]{\citep{chebi} Chemical Entities of Biological Interest (ChEBI) is a freely available dictionary of molecular entities focused on "small" chemical compounds. The database contains more than 56,000 compounds.}
\item[SRS]{\citep{srs} Substance Registry Services is the US EPA central system for information about substances that are tracked or regulated by EPA or other sources.}

@@

We use these data to retrieve basic information on the substances.
%
\begin{CodeChunk}
\begin{CodeInput}
R> etox_data <- etox_basic(ids$etoxid)
\end{CodeInput}
\end{CodeChunk}
%
\pkg{webchem} always returns a named list (one entry for each substance) and the available information content can be very voluminous.
Therefore, we provide extractor functions for the common identifiers: CAS, SMILES and InChIKeys.
%
\begin{CodeChunk}
\begin{CodeInput}
R> etox_cas <- cas(etox_data)
R> head(etox_cas)
\end{CodeInput}
\begin{CodeOutput}
       8668        8494        <NA>        8397        7240        7331 
 "105-67-9" "1570-64-5"          NA "1912-24-9"   "71-43-2" "6190-65-4" 
\end{CodeOutput}
\end{CodeChunk}
%
A variety of data are available and we cannot provide extractor
functions for each of those.  Therefore, if users need to extract
other data, they have to write simple extractor functions (see the
following examples).

>>>>

\begin{description}
\item[NIH Chemical Identifier Resolver (CIR)]{\citep{cir} A web
    service that converts from and to various chemical identifiers. The database holds millions of identifier combinations.}
\item[ChemSpider]{\citep{pence_chemspider:_2010} is a free chemical
	structure database providing access to over 67 million
	structures from hundreds of data sources. It provides identifiers, properties and can also be
	used to convert identifiers.}
\item[Chemical Translation Service (CTS)]{
  \citep{Wohlgemuth_Haldiya_Willighagen_Kind_Fiehn_2010} A web
    service that converts from and to various chemical identifiers.}
\item[ETOX]{\citep{etox} Information System Ecotoxicology and
    Environmental Quality Targets by the German Federal Environmental
    Agency. Provides basic identifiers, synonyms, ecotoxicological
    data for over 64,000 entries and quality targets for different countries.}
\item[ChemID\emph{plus}]{\citep{Tomasulo_2002} is a large web-based
	database provided by the National Library of Medicine. It contains
	identifiers, synonyms, toxicological data and chemical
	properties for over 420,000 records.}
\item[OPSIN]{\citep{Lowe_Corbett_Murray-Rust_Glen_2011} The Open
	Parser for Systematic IUPAC nomenclature is a chemical name
	interpreter and provides InChI and SMILES identifiers.}
\item[Compendium of Pesticide Common Names]{\citep{wood} The
	compendium provides information on pesticide common names,
	identifiers and classification. The compendium contains more than 1800 active ingredients and more than 350 ester and salt derivatives. }
\item[Wikidata]{\citep{wiki} Wikipedia contains information for over
	210,000 chemicals
	\citep{Ertl_Patiny_Sander_Rufener_Zasso_2015}.}
\item[PubChem]{\citep{Kim_2016} PubChem is a public repository for
    information on more than 250 million chemical substances, providing identifiers,
    properties and synonyms. We use an interface to the PUG-REST web
    service \citep{Kim_Thiessen_Bolton_Bryant_2015}.}
\item[PAN Pesticide Database]{ \citep{pan} Information on pesticides --
	provides basic identifiers, ecotoxicological data, chemical
	properties, uses and regulatory status for 6,500 pesticides.}
\item[Flavornet]{\citep{flavornet} Flavornet is a compilation of 738 aroma compounds found in human odor space.}
\item[NIST]{\citep{nist} The NIST Chemistry WebBook provides access to data compiled and distributed by NIST under the Standard Reference Data Program. The WebBook provides chemical and physical property data on over 40,000 compounds.}
\item[ChEBI]{\citep{chebi} Chemical Entities of Biological Interest (ChEBI) is a freely available dictionary of molecular entities focused on "small" chemical compounds. The database contains more than 56,000 compounds.}
\item[SRS]{\citep{srs} Substance Registry Services is the US EPA central system for information about substances that are tracked or regulated by EPA or other sources.}

@@

We use these data to retrieve basic information on the substances.
%
\begin{CodeChunk}
\begin{CodeInput}
R> etox_data <- etox_basic(ids$etoxid)
\end{CodeInput}
\end{CodeChunk}
%
When possible, \pkg{webchem} returns a data frame with one row per substance.  However, data from some sources can be very voluminous and not tabular. In these cases \pkg{webchem} always returns a named list (one entry for each substance).
Therefore, we provide extractor functions for the common identifiers: CAS, SMILES and InChIKeys.
%
\begin{CodeChunk}
\begin{CodeInput}
R> etox_cas <- cas(etox_data)
R> head(etox_cas)
\end{CodeInput}
\begin{CodeOutput}
       8668        8494        <NA>        8397        7240        7331 
 "105-67-9" "1570-64-5"          NA "1912-24-9"   "71-43-2" "6190-65-4" 
\end{CodeOutput}
\end{CodeChunk}
%
A variety of data are available and we cannot provide extractor
functions for each of those.  Therefore, if users need to extract
other data, they have to write simple extractor functions (see the
following examples).
